
# Loading...
```{r}
switch(Sys.info()[4]
       , Bakbeestje = setwd("~/Nextcloud/TUE/Current/2IMG10 - Topological Data Analysis/2img10-group-6")
       )

source("bootstrap.R")


```
Oeh, would this work?
```{zsh}
/usr/bin/echo "hellow"
```

Yes, yes it does. so Can I update the local repo from this?
```{zsh}
git pull 
```
And there is much rejoicing. 

# dataset maken
```{r}
belgie <- belgie_long %>%
  mutate(Country = "Belgium")
duitsland <- germany_long %>%
  mutate(Country = "Germany")
nederland <- infection_city %>%
  rename(dateRep = date, Cases = value) %>%
  mutate(Country = "Netherland") 

bal <- left_join(belgie, duitsland) %>%
  left_join(nederland) %>%
  mutate(dateRep = as_date(dateRep) ) 
baal_wider <- bal
bal <- bal %>%
  pivot_wider( names_from = dateRep, values_from = Cases) 


baal <-bal
for( i in 10:length(baal) ) {
  baal[i,] <- na.locf(baal[i,], na.rm = F)
}
baal <- baal %>%
  mutate( 
    across(everything() , ~replace_na(.x , 0))
  )
```
#Example of how it works. 
```{r}
distmatrix <- dist(data.frame(baal$Longitude, baal$Latitude))
filterValues <- baal$Longitude
nodelabel <- baal$City 

mapperThing <- mapper(dist_object = distmatrix,
                                filter_values = baal$Longitude,
                                num_intervals = 7,
                                percent_overlap = 25,
                                num_bins_when_clustering = 5)






MapperNodes <- mapperVertices(mapperThing, nodelabel )
MapperLinks <- mapperEdges(mapperThing)

forceNetwork(Nodes = MapperNodes, Links = MapperLinks, 
             Source = "Linksource", Target = "Linktarget",
             Value = "Linkvalue", NodeID = "Nodename",
             Group = "Nodename", opacity = 1, opacityNoHover = 1,
             linkDistance = 100, charge = -20,legend = TRUE,
             Nodesize = "Nodesize")  
```
# Things to change: dist, filter_values, nodelabel
```{r}

#####
distmatrix <- dist(data.frame(baal$Longitude, baal$Latitude))
filterValues <- baal$Longitude
nodelabel <- baal$City 
#####
plotForceFromDist(distmatrix, filterValues, nodelabel)

```

```{r}
print(baal_wider)
```
sumDeaths <- aggregate(infection_corona_world$deaths, by=list(Category=infection_corona_world$countriesAndTerritories), FUN=sum)

```{r}
print(baal_wider$dateRep[30])
start <- as.numeric(baal_wider$dateRep[30])
print(start)
TotalWeeklyCases <- baal_wider %>% filter(dateRep == start)
for(i in 1:7 ){
  temp <- baal_wider %>% filter(dateRep == start + i )
  TotalWeeklyCases <- rbind(TotalWeeklyCases, temp)
}
dfLatlong <- baal_wider %>%
  select( Country, City, Longitude, Latitude) %>%
  unique()
print(dfLatlong)


sumBaal <- aggregate(
    TotalWeeklyCases$Cases
  , by= list(Category=TotalWeeklyCases$City )
  , FUN=sum
) %>%
  rename(City = Category, Cases = x) %>%
  right_join(dfLatlong) 

#sumBaal$Category <- as_factor(sumBaal$Category)
#sumBaal$C <- as.integer(sumBaal$Category)
print(sumBaal)


#####
distmatrix <- dist(data.frame(baal_wider$Latitude, baal_wider$Longitude))
#filterValues <- baal_wider$Latitude
#nodelabel <- sumBaal$Category
```

```{r}
#distmatrix <- dist(data.frame(baal$Longitude, sumBaal$Cases))
filterValues <- sumBaal$Cases
filterValues <- baal$`2020-04-20`
#nodelabel <- baal$City 
#####
  mapperThing <- mapper(dist_object = distmatrix,
                        filter_values = filterValues,
                        num_intervals = 7,
                        percent_overlap = 25,
                        num_bins_when_clustering = 5)
  MapperNodes <- mapperVertices(mapperThing, nodelabel )
  MapperLinks <- mapperEdges(mapperThing)
  forceNetwork(Nodes = MapperNodes, Links = MapperLinks, 
               Source = "Linksource", Target = "Linktarget",
               Value = "Linkvalue", NodeID = "Nodename",
               Group = "Nodename", opacity = 1, opacityNoHover = 1,
               linkDistance = 100, charge = -20,legend = TRUE,
               Nodesize = "Nodesize")  
```